Hyperopt-Sklearn: Subtitle?

### 2014-04-26 papers/2014-automl/paper.tex
paper - URL footnote and conclusion

\begin{abstract}
    Hyperopt-sklearn is a new software project that provides automatic algorithm configuration of the Scikit-learn machine learning library.
    Following Auto-Weka, we take the view that the choice of classifier and even the choice of pre-processing module can be taken together to represent a {\em single large hyperparameter optimization problem}.
    We use Hyperopt to define a search space that encompasses many standard components (e.g. SVM, RF, KNN, PCA, TFIDF) and common patterns of composing them together.
    We demonstrate, using search algorithms in Hyperopt and standard benchmarking data sets (MNIST, 20-Newsgroups, Convex Shapes), that searching this space is practical and effective.
    In particular, we improve on best-known scores for the model space for both MNIST and Convex Shapes.
\end{abstract}
%\begin{keywords}
%Bayesian Optimization, Model Selection, Hyperparameter Optimization, Scikit-learn
%\end{keywords}

@@

@@

>>>>

\begin{abstract}
    Hyperopt-sklearn\footnote{Hyperopt-Sklearn home: http://github.com/hyperopt/hyperopt-sklearn} is a new software project that provides automatic algorithm configuration of the Scikit-learn machine learning library.
    Following Auto-Weka, we take the view that the choice of classifier and even the choice of pre-processing module can be taken together to represent a {\em single large hyperparameter optimization problem}.
    We use Hyperopt to define a search space that encompasses many standard components (e.g. SVM, RF, KNN, PCA, TFIDF) and common patterns of composing them together.
    We demonstrate, using search algorithms in Hyperopt and standard benchmarking data sets (MNIST, 20-Newsgroups, Convex Shapes), that searching this space is practical and effective.
    In particular, we improve on best-known scores for the model space for both MNIST and Convex Shapes.
\end{abstract}
%\begin{keywords}
%Bayesian Optimization, Model Selection, Hyperparameter Optimization, Scikit-learn
%\end{keywords}

@@

We have introduced Hyperopt-sklearn, a Python package for automatic algorithm configuration of standard machine learning algorithms provided by Scikit-Learn.
Hyperopt-sklearn provides a unified view of 6 possible preprocessing modules and 6 possible classifiers, yet with the help of Hyperopt's optimization functions
it is able to both rival and surpass human experts in algorithm configuration.

@@

%%
%%
%%
%%
%%
